Supplementary methods

### 2020-08-29 code/figure6.Rmd
Add alpha values to figure6, Add SM3 to methods

## Getting n_race for white and black
cancerdat <- read_csv("../data/survival/clinical_plus_cluster.csv")
cancer.clusttype <- cancerdat %>% dplyr::select(type, race, clust_knn) %>% ## select relevant columns
  filter(race %in% c("WHITE", "BLACK OR AFRICAN AMERICAN")) ## filter black and white only
cancer.race <- as.data.frame(table(cancer.clusttype$type)) ## table cancer type
cancer.race$facetname <- paste0(cancer.race$Var1, " (N = ", cancer.race$Freq, (")")) ## Create a new col with type and freq together
cancer.race$Freq <- NULL ## Remove Freq Column
names(cancer.race) <- c("tiss", "facetname") ## rename cols for left join in kclassplot below

## Getting n_cluster within cancer.type
cancer.nclustintype <- as.data.frame(table(cancer.clusttype$type, cancer.clusttype$clust_knn))
cancer.nclustintype <- cancer.nclustintype %>% mutate(alpha = case_when(Freq < 10 ~ "0.05",
                                                                        Freq >= 10 & Freq < 25 ~ "0.5",
                                                                        Freq >= 25 ~ "1.0"))
textlist <- list()
cancertype <- "BRCA"
for(n in cancertype) {
  df <- cancer.nclustintype %>% filter(Var1 == n)
  cancer.race$lab <- as.character(paste(df[1, "alpha"], "\n",df[2, "alpha"], "\n", df[3, "alpha"], "\n",df[4, "alpha"], "\n",df[5, "alpha"], "\n",df[6, "alpha"], "\n",df[7, "alpha"], "\n",df[8, "alpha"], "\n",df[9, "alpha"], "\n",df[10, "alpha"]))
}

textlist <- as.data.frame(do.call(rbind, textlist))

tisnames <- levels(cancerdat$type)

@@

	## 
	dfclas <- left_join(dfclas, cancer.race, by = "tiss")

	## Plotting
	ggplot(dfclas,aes_(x = quote(value),y = quote(class), fill = quote(class))) + geom_density_ridges() +
		facet_wrap(. ~ facetname,nrow=3) + theme_minimal() + scale_fill_brewer(palette = "Paired") +
		xlim(0,3) + theme(legend.position = "none") + ggtitle("Class Specific Coefficients") +
	  labs(x = expression(paste("k"["cl"])), y = "Cluster Identity") +
	  geom_text(data = dfclas, aes(label = lab), x = 2.5, y = 6) +
	  mytheme + turn.off.legend +scale_fill_manual(values = cluster.colours)
```

>>>>

## Getting n_race for white and black
cancerinfo <- read_csv("../data/survival/clinical_plus_cluster.csv")
cancer.clusttype <- cancerinfo %>% dplyr::select(type, race, clust_knn) %>% ## select relevant columns
  filter(race %in% c("WHITE", "BLACK OR AFRICAN AMERICAN")) ## filter black and white only
cancer.race <- as.data.frame(table(cancer.clusttype$type)) ## table cancer type
cancer.race$facetname <- paste0(cancer.race$Var1, " (N = ", cancer.race$Freq, (")")) ## Create a new col with type and freq together
cancer.race$Freq <- NULL ## Remove Freq Column
names(cancer.race) <- c("tiss", "facetname") ## rename cols for left join in kclassplot below

## Getting n_cluster within cancer.type to calculate alpha
cancer.nclustintype <- as.data.frame(table(cancer.clusttype$type, cancer.clusttype$clust_knn)) ## Determine n_cancer in each cluster
cancer.nclustintype <- cancer.nclustintype %>% mutate(alpha = case_when(Freq < 10 ~ 0.1, ## Create alpha column for geom_ridges
                                                                        Freq >= 10 & Freq < 25 ~ 0.5,
                                                                        Freq >= 25 ~ 1.0),
                                                      alphatext = case_when(Freq < 10 ~ "0.1", ## Create alpha text for labeling
                                                                        Freq >= 10 & Freq < 25 ~ "0.5",
                                                                        Freq >= 25 ~ "1.0"))

cancer.alpha <- cancer.nclustintype %>% dplyr::select(Var1, Var2, alphatext) %>%
  'colnames<-' (c("tiss", "class","alphatext"))

tisnames <- levels(cancerdat$type) ## getting cancer type names

# Code to generate the text label for each alpha
# textlist <- list() ## create list for for loop
# for(n in tisnames) {
#   df <- cancer.nclustintype %>% filter(Var1 == n) ## Filter for specific cancer type
#   textlist[[n]] <- as.character(paste(df[1, "alphatext"], "\n",df[2, "alphatext"], "\n", df[3, "alphatext"], "\n",df[4, "alphatext"], "\n",df[5, "alphatext"], "\n",df[6, "alphatext"], "\n",df[7, "alphatext"], "\n",df[8, "alphatext"], "\n",df[9, "alphatext"], "\n",df[10, "alphatext"])) ## collect all the alpha values and insert new line after each alpha
# }
# textlist <- as.data.frame(do.call(rbind, textlist)) ## rbind list
# textlist <- textlist %>% 'colnames<-' ("lab") %>% ## rename col to lab
#   rownames_to_column(var = "tiss") ## cancer type to column for left join

@@

## Left joining data created above
dfclas <- left_join(dfclas, cancer.race, by = "tiss") ## add facet names

# ## Code for adding alpha level text
# 	dfclas <- left_join(dfclas, textlist, by = "tiss")
# 	for(n in tisnames) {
# 	  dfclas[which(dfclas$tiss == n)[-1], "lab"] <- NA ## Remove the extra 29999 labels that will be generated on the ggplot
# 	}

## Code for setting alpha in geom_density ridges
alpha.setup <- c() ## create empty vector for loop
	for(n in tisnames) { ##loop through the cancer type in alphabetical order
	  df <- cancer.nclustintype %>% filter(Var1 == n) %>% ## Filter for specific cancer type	
	    arrange(desc(Var2)) ## Arrange in desc order cause thats how the alpha are set from 10 <- 1
	  for(p in 1:nrow(df)) { ## loop through the clusters starting from 10 --> 1
	    alpha.setup <- c(alpha.setup, rep(df[p, "alpha"], 512)) ## Get the alpha value for each cluster in each cancer type and rep 512 (necessary for geom ridges)
	  }
	}

	## Plotting
	ggplot(dfclas,aes_(x = quote(value),y = quote(class), fill = quote(class))) + geom_density_ridges(alpha = alpha.setup) +
		facet_wrap(. ~ facetname,nrow=3) + theme_minimal() + scale_fill_brewer(palette = "Paired") +
		xlim(0,3) + theme(legend.position = "none") + ggtitle("Class Specific Coefficients") +
	  labs(x = expression(paste("k"["cl"])), y = "Cluster Identity") +
	  #geom_text(data = dfclas, aes(label = lab), x = 2.5, y = 6) +
	  mytheme + theme(plot.title= element_text(hjust = 0.5))+ turn.off.legend +
	  scale_fill_manual(values = cluster.colours)
```

### 2020-08-29 text/supplemental_methods.Rmd
Add alpha values to figure6, Add SM3 to methods

**Supplementary Figure SM3: Priors for the tissue and class coefficients** The tissue coefficient
is chosen to admit parameter values across a range from near 0 to 20+
in the high density region, reflecting the wide variety of severities
across tissue type. Within a given tissue, the class k parameter
multiplies the tissue k and is given a peak density at 1, and a
credible range from near 0 to 5, reflecting our expectation of a
moderate amount of variation across the classes.

>>>>

**Supplementary Figure SM3: Priors for the tissue and class coefficients.** The tissue coefficient
is chosen to admit parameter values across a range from near 0 to 20+
in the high density region, reflecting the wide variety of severities
across tissue type. Within a given tissue, the class k parameter
multiplies the tissue k and is given a peak density at 1, and a
credible range from near 0 to 5, reflecting our expectation of a
moderate amount of variation across the classes.
